Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-24 manuscript.Rmd
LENA stuff

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features of the method that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions [CITES], the current investigation takes a needed step forward by testing accuracy over long recordings.

## Inspiration from Long-Form Audio Recordings

>>>>

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions [CITES], the current investigation takes a needed step forward by testing accuracy over long recordings.

## Inspiration from Long-Form Audio Methods

The LENA&reg; recorder is a commercial device that is worn by infants in a custom shirt pocket that has sufficient battery life and storage to record for an entire day. Closed-source LENA&reg; algorithms analyze the audio recordings to provide counts of useful metrics, such as the number of words spoken by adults in the vicinity of the participant. Other long-form audio methods rely on custom-built recorders [@WassPhillips2022], apply alternative classification algorithms to LENA&reg; data [@RasanenSeshadri2020; @MichelettiYao2022], or manually transcribe audio recorded by LENA&reg; devices to improve accuracy or identify behaviors beyond the built-in categories [@Bergelson2019Corpus; @MendozaFausey2021].

Long-form audio recordings have had a transformational impact on language development by allowing researchers to characterize opportunities for learning in daily life. Measuring the amount of speech heard by infants in the home [@Weisleder2013] or in a daycare setting [@PerryPrince2018] revealed individual differences input that predict later vocabulary. Full-day language recording synchronized with other data sources allows researchers to identify how vocal input and production interacts with other processes. Beyond individual differences in aggregated data, long-form recordings can be used to determine the temporal schedule of experiences. For example, infants' daily experiences hearing music are clustered in time, with "bursty" episodes of hearing music separated by relatively long periods during which music is absent [@MendozaFausey2022]. Synchronizing audio recordings with other data sources extends researchers' ability to characterize daily experiences. Linking LENA&reg; speech measurements to repeated, time-stamped text-message surveys about infant device placement revealed that infants heard less caregiver speech during moments that they were restrained in devices such as swings, exersaucers, and car seats [@MalachowskiSalo2023]. A custom-built wearable ECG and audio recorder allowed @WassPhillips2022 to discover that infant arousal increases the likelihood of infant vocalization across the day. The ability to record real-time, synchronized data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants.

Key features
- unobtrusive (Bergelson; CTL stuff)
- mobile (no limits to where recording happens)
- real time
- long duration (capture entire day and heterogeniety in activities)
- automatic classification with good-enough accuracy (scaling)

### 2023-02-24 manuscript.tex
LENA stuff

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features of the method that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions {[}CITES{]}, the current investigation takes a needed step forward by testing accuracy over long recordings.

\hypertarget{inspiration-from-long-form-audio-recordings}{%
\subsection{Inspiration from Long-Form Audio Recordings}\label{inspiration-from-long-form-audio-recordings}}

@@

@@

>>>>

In this paper, we present an inertial sensing method to classify infant body position from moment-to-moment across an entire day, and validate its accuracy using XX hours of video recorded across XX in-home data collection sessions. Our method takes inspiration from a more mature technology: Long-form audio recordings of infants' language experiences using wearable audio recorders such as the LENA device. We begin by describing the impact of long-form audio recordings on research in developmental psychology, and identify the key features that should be replicated in long-form recordings of motor behavior. Next, we review the current state-of-the-art in measuring infant motor behavior---video and survey data---and their limitations in capturing real-time, full-day behavior. Finally, we discuss the advantages of using inertial sensing to classify motor behavior. Despite promising past results in brief sessions {[}CITES{]}, the current investigation takes a needed step forward by testing accuracy over long recordings.

\hypertarget{inspiration-from-long-form-audio-methods}{%
\subsection{Inspiration from Long-Form Audio Methods}\label{inspiration-from-long-form-audio-methods}}

Impactful findings (Hailey write this paragraph)
- individual differences in experiences
- distribution of experiences (burstiness)
Full-day language recording synchronized with other data sources allows researchers to identify how vocal input and production interacts with other processes. Linking LENA® speech measurements to repeated, time-stamped text-message surveys about infant device use revealed that infants heard less caregiver speech during moments that they were restrained in devices such as swings, exersaucers, and car seats (Malachowski et al., 2023). A custom-built wearable ECG and audio recorder allowed Wass et al. (2022) to discover that infant arousal increases the likelihood of infant vocalization across the day. In both examples, the ability to record real-time, synchronized data is vital for making inferences about processes that happen on the timescale of minutes or even seconds within in an individual as opposed to comparisons of aggregated data between infants.

Key features
- unobtrusive (Bergelson; CTL stuff)
- mobile (no limits to where recording happens)
- real time
- long duration (capture entire day and heterogeniety in activities)
- automatic classification with good-enough accuracy (scaling)

@@

\leavevmode\vadjust pre{\hypertarget{ref-MalachowskiSalo2023}{}}%
Malachowski, L. G., Salo, V. C., Needham, A. W., \& Humphreys, K. L. (2023). Infant placement and language exposure in daily life. \emph{Infant and Child Development}. \url{https://doi.org/10.1002/icd.2405}

@@

\leavevmode\vadjust pre{\hypertarget{ref-WassPhillips2022}{}}%
Wass, S., Phillips, E., Smith, C., Fatimehin, E. O., \& Goupil, L. (2022). Vocal communication is tied to interpersonal arousal coupling in caregiver-infant dyads. \emph{{eLife}}, \emph{11}. \url{https://doi.org/10.7554/elife.77399}
